---
title: "Data Visualization Using `{ggplot2}`"
subtitle: "Week 9 Lecture 2"
author: "Your Name"
format: 
  html:
    -embed-resources: true
---

```{r}
#| message: false

library(tidyverse)

library(janitor)

library(palmerpenguins)

library(readxl)

library(gapminder)

library(DT)

conflicted::conflicts_prefer(palmerpenguins::penguins)

conflicted::conflicts_prefer(dplyr::filter)
```

## Introduction

In COR 14X, we learned to visualize **numerical data** using **histograms**, and **categorical data** using **bar charts**. **Scatter plots** are used to visualize the **relationship between two numerical variables**, and **box plots** are used to visualize **numerical data across groups**.

We will primarily use `{ggplot2}` package to generate plots. The `gg` in `{ggplot2}` stands for **grammar of graphics**. 

## Histogram

**Example 1.** Plot the penguins' body mass.

*Method 1:* Using base R.

```{r}
plot_1a <- hist(penguins$body_mass_g)

plot_1a
```

*Method 2:* Using `{ggplot2}`.

```{r}
plot_1b <- penguins |> 
  ggplot(
    aes(x = body_mass_g)
  ) +
  geom_histogram()

plot_1b
```

```{r}
plot_1c <- penguins |> 
  ggplot(
    aes(x = body_mass_g)
  ) +
  geom_histogram(
    binwidth = 500,
    fill = 'skyblue',
    color = 'blue'
  ) +
  labs(
    title = "Distribution of Penguins' Body Mass",
    x = 'Body Mass (g)',
    y = 'Count'
  )

plot_1c
```

```{r}
plot_1c +
  theme_bw()
```

```{r}
plot_1c +
  theme_classic()
```

```{r}
plot_1d <- penguins |> 
  ggplot(
    aes(x = flipper_length_mm)
  ) +
  geom_histogram(
    binwidth = 5,
    color = '#A90533',
    fill = '#F08DA8'
  ) +
  labs(
    title = "Distribution of Penguins' Flipper Length",
    x = 'Flipper Length (mm)',
    y = 'Count'
  ) +
  theme_classic()

plot_1d
```