---
title: "Vectorization"
author: "Your Name"
format: 
  html:
    embed-resources: true
---

```{r}
#| message: false

library(tidyverse)

library(palmerpenguins)
```

Previously, we saw that one can perform mathematical operations on a vector’s name rather than applying the same operations to each of its elements. These types of operations are called **___**. Vectorization includes statistical operations as well as mathematical operations.

**Example 1.** From the `penguins` dataset, define `bw` to be the penguins' body mass. Find the following:

(a) The number of observations in the vector `bw`.
(b) Convert the body mass from grams to kilograms.
(c) Convert the body mass from grams to pounds.
(d) Find the mean body mass.
(e) Find the standard deviation of the body mass.
(f) Find the variance of the body mass.
(g) Find the five-number summary of the body mass.

*Answer.* First, let's view the `penguins` dataset.

```{r}
```

Next, let's extract the `body_mass_g` column form `penguins` and name it `bw`.

```{r}
```

(a) Recall that `length()` tells us the number of elements in a vector.

```{r}
```

(b) To convert g to kg, note that 1 g = 0.001 kg.

```{r}
```

(c) To convert g to lb, note that 1 g is roughly equal to 0.00022 lb.

```{r}
```

(d) To find the mean body mass, we use the `mean()` function.

```{r}
```

What happened in the above calculation? Why do you think this happened?

```{r}
```

(e) Use `sd()` to find the standard deviation of `bw`.

```{r}
```

(f) Use `var()` to find the variance of `bw`.

```{r}
```

(g) Use `summary()` to find the five-number summary of `bw`.

```{r}
```

**Exercise 1.** Define `fl` to be the flipper length column from penguins, and repeat the calculations from Example 1. For parts (b) and (c), convert the length from millimeters to centimeters and inches, respectively.

(a)

```{r}
```

(b)

```{r}
```

(c)

```{r}
```

(d)

```{r}
```

(e)

```{r}
```

(f)

```{r}
```

(g)

```{r}
```

## Vectorized Logical Operations

We can similarly extend logical operations to vectors, as we did with mathematical and statistical operations.

**Example 2.** Find the body masses from `penguins` that are less than or equal to 3,550 g.

```{r}
```

**Exercise 2.** Find the flipper lengths from `penguins` that are greater than or equal to 197 mm.

```{r}
```

**Example 3.** Find the body masses from `penguins` that are greater than the mean.

```{r}
```

**Exercise 3.** Find the flipper lengths from `penguins` that are less than or equal to the median.

```{r}
```

:::{.callout-warning}
The outputs of Example 2 and Exercise 2 do not explicitly identify which penguins satisfy the required conditions. We will discuss how to circle this square later.
:::

## The `%in%` Operator

If one wishes to find the body masses that are equal to the mean body mass, then the appropriate logical operation is:

```{r}
```

What if we want the body masses that are equal to the mean or the median body mass? The amounts to comparing the body masses to a _list_ of values. To achieve this, we use the `%in%` operator.

```{r}
```

The last line in the code chuck above can be translated as: "Find the body masses that are in a list, this list is the mean and the median body mass."

**Exercise 4.** Find the flipper lengths that are the minimum or the maximum flipper lengths.

```{r}
```