---
title: "CIS 351 B: Week 2 Lecture 2"
author: "Your Name"
format: 
  html:
    embed-resources: true
---

## Defining Variables in R

One of the main features of coding in R is the ability to define **objects** or **variables**. Creating a variable involves giving a name to an object, allowing you to reference the object by name later.

The symbol we use to perform variable assignment is `<-`.


**Example 1.** Consider the first 20 places after the decimal point for $\pi$.


```{r}
p <- 3.14159265358979323845

p^2

cos(p/2)
```

**Example 2.** Find the mean, standard deviation, and the variance of the sequence 2, 3, 5, 7, 11, 13, 17, 19, 23.


```{r}
P <- c(2, 3, 5, 7, 11, 13, 17, 19, 23)

mean(P)

(2 + 3 + 5 + 7 + 11 + 13 + 17 + 19 + 23)/9

sd(P) # evaluate the standard deviation of the sequence P

var(P) # evaluate the variance of the of the sequence P
```

## Variable Assignment Convention

In general, we will use the "lower snake case" for variable names. The lower snake case is a convention where words are all in lower cases and words are separated by the underscore symbol `_`.