---
title: "CIS 351 B: Week 3 Lecture 1"
author: "Your Name"
format: 
  html:
    embed-resources: true
---

## Data Types in R

In general, there are three data types in R.

* **Numeric:** numbers, e.g., `1`, `1/2`, `pi`, `3e-10`.

* **Characters:** generic texts (letters or symbols or numbers), e.g., `"Flagler"`, `"John Doe"`, `"X17_Y19"`.

* **Logical (Boolean):** binary values corresponding to `TRUE` or `FALSE`.

We can use the `class()` function to determine the data type of a variable.

### Numeric Values

```{r}
class(1)
```
```{r}
class(1/2)
```

```{r}
class(pi)
```

```{r}
p <- pi^2/200

class(p)
```

### Character Values

```{r}
"mango"

class("mango")
```

```{r}
s <- "I like mangos."

class(s)
```

**Example 1.** What is the data type of `"1"`?

```{r}
class("1")
```

```{r}
class("09/08/2025")
```

::: {.callout-important}
Character values are always wrapped around by quotation marks.
:::

### Logical Values

```{r}
class(TRUE)

class(FALSE)
```

```{r}
1 == 2
```

```{r}
sin(pi/4) == cos(pi/4)
```
```{r}
1 < 2
```