---
title: "CIS 351 B: Week 2 Lecture 1"
author: "Your Name"
format: html
---

## Code Comments

Code comments allow us to explain the R code that we have written. It will also make your R code easier for someone else to read. In order to write comments in an R code chunk, we start with the `#` symbol, followed the comment.

**Example 1.** Evaluate cosine of pi/2 and write a code comment for your R code.

```{r}
cos(pi/2) # this line of code evaluates cosine of pi/2
```

## Scientific Notation in R

R uses `e` to denote powers base 10. So in the previous example, R evaluated $\cos(\pi/2)$ to be `6.123e-17`. This should be interpreted as $6.123 \times 10^{-17} = 0.00000000000000006123$, but this can be interpreted as 0.

**Example 2.** Evaluate $\pi^{200}$.


```{r}
pi^(200) # this evaluates pi^200.
```

## Mathematical/Statistical Functions in R

**Example 3.** Evaluate log(10).

```{r}
log(10)
```

```{r}
log(10, 10)
```

*Remark:* The `log()` function in R is base e, i.e., it is the natural log function. We specify a different base by typing a second argument inside `log()`.

```{r}
penguins <- penguins

mean(penguins$body_mass_g, na.rm = TRUE) # computes the mean body mass of penguins

sd(penguins$body_mass_g, na.rm = TRUE) # computes the standard deviation of penguins' body mass
```