---
title: "CIS 351: Week 3 Lecture 2"
author: "Your Name"
format: 
  html:
    embed-resources: true
---

## Logical Values (continued)

Internally, R evaluates `TRUE` as the numeric value 1 and `FALSE` as 0.

```{r}
```

```{r}
```

## `NA` Values

In R, empty entries in a data set are represented by `NA`, a special type of object used to indicate missing values.

```{r}
```

`NA` behaves differently compared to other data types (even `TRUE` and `FALSE`).

```{r}
```

```{r}
```

In R, summary statistics cannot be calculated when a data set contains `NA` values. We will revisit this point when we discuss methods for handling and removing `NA`s.

## Asking Questions With Logical Operations

Mathematical equality and inequalities are considered as **logical operators** in R. You can use them to determine whether a statement is `TRUE` or `FALSE`.

```{r}
# is 3 = 4?

```

```{r}
# are apple and orange the same data value?

```

In R, the `!` symbol is used as a negate the truth value of a statement. The symbol for "not equal to" is `!=`.

```{r}
```

```{r}
```

Below is a summary of the logical operators and their respective symbols in R.
* "equal to":
* "not equal to":
* "(strictly) less than":
* "(strictly) greater than":
* "less than or equal to":
* "greater than or equal to"
