---
title: "Introduction to Data Visualization"
subtitle: "Week 11 Lectures 1"
author: "Your Name"
format: 
  html:
    -embed-resources: true
---

```{r}
#| message: false
#| warning: false

library(tidyverse)

library(janitor)

library(palmerpenguins)

library(readxl)

library(gapminder)

library(gt)

library(datasauRus)

library(ggpubr)

conflicted::conflicts_prefer(palmerpenguins::penguins)

conflicted::conflicts_prefer(dplyr::filter)
```

# Boxplot

Boxplots are a great way to visualize the distribution of a continuous variable across different categories. They display the median, quartiles, and potential outliers in the data.

**Example 1.** Visualize the distribution of flipper lengths across different penguin species.

```{r}
```

One can easily change the boxplot from vertical to horizontal by adding the `coord_flip()` function.


```{r}
```

## Boxplot With Dots

Adding individual data points to a boxplot can provide additional context about the distribution of the data. This can be done using `geom_jitter()`.


```{r}
```

# Scatterplot

Scatterplots are used to visualize the relationship between two continuous variables. They can help identify correlations, trends, and potential outliers in the data. Normally, we use `geom_point()` to create scatterplots. However, we often need to add additional information to the plot, we will use the `{ggpubr}` package.

**Example 2.** Visualize the relationship between flipper length and body mass in penguins.

```{r}
```

**Example 2.** Add a regression line to the scatterplot to visualize the trend.

```{r}
```

**Example 3.** Summarize the `datasaurus_dozen` dataset to compute the mean, median, standard deviation, and variance for both `x` and `y` variables, grouped by the `dataset` variable. Based on the summary statistics, what can you say about these different datasets?

```{r}
```

```{r}
```