---
title: "Vectors in R"
author: "Your Name"
format: 
  html:
    embed-resources: true
---

## Vectors

R allows us to work with multiple data values at once. A **vector**-—the most fundamental data structure in R—-is essentially an ordered collection of elements. To create a vector, we use the `c()` function. A vector is often referred to as a **list** or a **set**.

**Example 1.** Create a vector of heights 156, 170, 177, 180, 180, 182.
```{r}
```

**Exercise 1.** What is the data type of `height`?

```{r}
```

**Example 2.** Create a vector of the world's oceans.
```{r}
# a list of characters
```

**Exercise 2.** What is the data type of `oceans`?

```{r}
```

We can create a vector with mixed values.

```{r}
```

There is an inherent hierarchy to data types in R: **Character > Numeric > Logical**

To find out the number of elements in a vector, we use the `length()` function.

**Example 3.** How many elements are there in `heights`?

```{r}
```

**Exercise 3.** How many elements are there in `oceans`?

```{r}
```

## Working with Vectors

By working with variable names, we can perform operations on all the elements of a given vector.

**Example 4.** Subtract 10 from every element in `heights`.

```{r}
```

**Exercise 4.** Find the log of every element in `heights`.

```{r}
```