---
title: "Introduction to Data Visualization"
subtitle: "Week 11 Lectures 1"
author: "Your Name"
format: 
  html:
    -embed-resources: true
---

```{r}
#| message: false
#| warning: false

library(tidyverse)

library(janitor)

library(palmerpenguins)

library(readxl)

library(gapminder)

library(gt)

library(datasauRus)

library(ggpubr)

conflicted::conflicts_prefer(palmerpenguins::penguins)

conflicted::conflicts_prefer(dplyr::filter)
```

# Line Graphs

Line graphs are used to display trends over time or ordered categories. They are particularly useful for showing how a variable changes continuously.

**Example 1.** Create a line graph to show the trend of population growth over time in the US.

Step 1. Load and clean the data.

```{r}

```

Step 2. Create the line graph.

```{r}

```

Step 3. Customize the graph.

```{r}

```

**Example 2.** Create a line graph to show the population growth over time for the US and _____.

Step 1. Load and clean the data.

```{r}

```

Step 2. Create the line graph.

```{r}

```

Step 3. Customize the graph.

```{r}

```